### 2021-04-20 introduction.tex
Final changes?

Our aim is to develop a more expressive version of GV while maintaining deadlock freedom. We chose GV for several reasons, some of which apply more generally as benefits to working within a concurrent $\lambda$-calculus as opposed to a name-passing process calculus. Concurrent $\lambda$-calculi support higher-order functions, and have a capability for abstraction not usually present in process calculi. Within a concurrent $\lambda$-calculus, one can derive extensions of the communication capabilities of the language via well-understood extensions of the functional fragment, \eg, we can derive internal/external choice from sum types. Concurrent $\lambda$-calculi maintain a clear separation between the program which the user writes and the configurations which represent the state of the system as it evaluates the program. However, our main motivation is that results obtained for $\lambda$-calculi transfer more easily to real-world functional programming languages. Case in point: we easily adapted the type system of PGV to Linear Haskell~\cite{bernardyboespflug18}, which gives us a library for deadlock-free session-typed programming~\cite{kokkedardha21hs}. %For us, these advantages outweigh the benefits of process calculi, \eg, their succinctness.
The benefit of working specifically with GV, as opposed to other concurrent $\lambda$-calculi, is its relation to CP~\cite{wadler14}, and its formal properties, including deadlock freedom. We thus pose our research question for GV:
\begin{quotation}
  \textbf{RQ:}
  Can we design a more expressive GV which guarantees deadlock freedom for cyclic-structured processes?
\end{quotation}

>>>>

Our aim is to develop a more expressive version of GV while maintaining deadlock freedom. While process calculi have their advantages, \eg, their succinctness, we chose to work with GV for several reasons. In general, concurrent $\lambda$-calculi support higher-order functions, and have a capability for abstraction not usually present in process calculi. Within a concurrent $\lambda$-calculus, one can derive extensions of the communication capabilities of the language via well-understood extensions of the functional fragment, \eg, we can derive internal/external choice from sum types. Concurrent $\lambda$-calculi maintain a clear separation between the program which the user writes and the configurations which represent the state of the system as it evaluates the program. However, our main motivation is that results obtained for $\lambda$-calculi transfer more easily to real-world functional programming languages. Case in point: we easily adapted the type system of PGV to Linear Haskell~\cite{bernardyboespflug18}, which gives us a library for deadlock-free session-typed programming~\cite{kokkedardha21hs}.
The benefit of working specifically with GV, as opposed to other concurrent $\lambda$-calculi, is its relation to CP~\cite{wadler14}, and its formal properties, including deadlock freedom. We thus pose our research question for GV:
\begin{quotation}
  \textbf{RQ:}
  Can we design a more expressive GV which guarantees deadlock freedom for cyclic-structured processes?
\end{quotation}
